\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{amsmath,amssymb,epsfig}

\title{Discrete Math Midterm: Practice Test 1}
\author{Maggie Lai}

\begin{document}

\maketitle



\section{Logic}

\subsection{Equivalence - Truth Tables}
Show that $((\neg (q\lor r)) \lor (\neg q \land r) ) \to \neg p$ is equivalent to $p\to q$ through a truth table.

\vspace*{3cm}

\subsection{Equivalence - Using Laws of Proposition Logic}
Show that $((\neg (q\lor r) ) \lor (\neg q \land r) ) \to \neg p$ is equivalent to $p\to q$ using the laws of propositional logic.

\vspace*{3cm}

\subsection{Quantifiers - Translation}
Express the following sentence as a logic formula with quantifiers:
\begin{center}
    It's possible for two negative integers to have an even sum that is at least -6.
\end{center}

\vspace*{1cm}

This is a universal/existential statement (circle one).

\subsection{Quantifiers - Negation}
Negate the logic formula from the last question so that it does not contain any negation operators $\neg$.

\vspace{1cm}

\section{Rules of Inference}
Consider the following set of premises:
\begin{itemize}
    \item My cat's name is Victor or Dipen.
    \item If my cat's name is Dipen, I also have a dog.
    \item I don't have a dog.
\end{itemize}
Use the rules of inference to infer "My cat's name is Victor." You may use the rules in Zybooks table 3.8 and table 1.5.1 (they will be projected on the board during the test).

\newpage
\section{Functions}
Let $f(x) = \sin(\pi x)$.
\subsection{Injectivity}
Give a domain for which $f$ is injective, and use the definition to state why it is injective on this domain.

\vspace{3cm}

\subsection{Surjectivity}
Give a codomain for which $f$ is surjective, and use the definition to state why it is surjective on this codomain.

\vspace{3cm}

\subsection{Bijectivity}
Give a domain and codomain for which $f$ is bijective, and use the definition to state why it is bijective on this range.
\begin{center}
    $f:$ \hspace{1.5cm} $\to$         
\end{center}

\newpage

\section{Proofs}
\subsection{Proof by cases}
Consider the theorem below:
\begin{center}
    \textbf{Theorem:} For all real numbers $x$ such that $x < -1$ or $x>1$, $x^2 > 1$.
\end{center}
Prove the theorem using a proof by cases.

\vspace{6cm}

\subsection{Proof by contrapositive}
Consider the theorem below:
\begin{center}
    \textbf{Theorem:} For all $mn\in \mathbb{R} - \mathbb{Q}$, $m$ is irrational or $n$ is irrational.
\end{center}
Prove the theorem using a proof by contrapositive.

\newpage

\section{Sets}
Please use these sets to fill in the blanks below:

Let $X =$ \{places that Tulane students live\}

Let $A = $ \{Sharp, Monroe, Butler, Wall, Warren\}

Let $B =$ \{Lake, River, Aron, DeLa, Weatherhead, Greenbaum\}

Let $C =$ \{Butler, Weatherhead\}

\begin{itemize}
    \item $(A \cup B) - C = $
    \item I live \hspace{2cm} if I live in $A \cap B$
    \item $|B - C| = $
    \item $|2^{B} \cup 2^{C}| = $
\end{itemize}

\section{Functional Completeness}
Define the logical operator $\not\to$ as the negation of the $\to$ operator. Show that $\{\to, \not\to\}$ is functionally complete.

\newpage

\section{Summations}
Let $\sum_{i=2}^8 2i-2$ be a finite sum.

\subsection{Summation Notation}
Rewrite the sum with the following indices:
$$\sum_{i=1}^7 $$
\vspace{3cm}

\subsection{Summation Value}
Calculate the value of the expression.

\vspace{3cm}

\subsection{Summation Expansion}
Write out the summation with addition (eg. 1 + 2 + 3 + ... + 10 for $\sum_{i=1}^{10} $)
\end{document}
